R code for 'Blood parasite infection causes marginal temporary costs in juvenile birds of prey

### 2025-02-21 MS_physiology_infection.Rmd
Add files via upload

```{r packages, message=F, warning=F}
library(chron)
library(cowplot)
library(EnvStats)
library(lme4)
library(lmerTest)
library(lsmeans)
library(ggalt)
library(ggdist)
library(ggeffects)
library(ggplot2)
library(ggpubr)
library(ggrepel)
library(ggridges)
library(ggsci)
library(ggsignif)
library(grid)
library(gridExtra)
library(magrittr)
library(patchwork)
library(plyr)
library(rptR)
library(RVAideMemoire)
library(sjPlot)
library(sjlabelled)
library(sjmisc)
library(tidybayes)
library(tidyverse)
library(wesanderson)
library(car)
## set theme for ggplot objects
theme_set(theme_tidybayes() + panel_border())
```

@@

## Panel wrapping Fig2 a & b:
## ----------------------------------------------------------------------------- 
Fig2 <-  Fig_2A +Fig_2B+
  plot_annotation(tag_levels = 'a') + 
  theme(plot.tag = element_text(size = 22, face = "bold"))

@@

  ggplot(mod_bc2) + 
  aes(x,predicted) + 
  geom_hline(yintercept = mean(mod_bc2$predicted, na.rm = T), 
             linetype = "dashed") + 
  labs(x = "", 
       y = "Body condition at T1") + 
  geom_errorbar(aes(ymin = mod_bc2$conf.low,
                    ymax = mod_bc2$conf.high),
                colour = "black",
                size = 2, 
                width = .1) +
  geom_errorbar(aes(ymin = mod_bc2$predicted - mod_bc2$std.error,
                    ymax = mod_bc2$predicted + mod_bc2$std.error),
                size = 8,
                colour = wes_palette("Zissou1",4),
                width = 0,) +
  geom_point(color = "black", 
             size = 2) + 
  theme_classic() + 
  theme(legend.position = "none",
        axis.title = element_text(size = 18),
        axis.text = element_text(size = 16),
        axis.line.x = element_blank(),
        axis.ticks.x = element_blank(),
        plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_text(hjust = 0.5, face = "bold")) + 
  geom_segment(size = .8, 
               aes(x = 1, 
                   y = max(mod_bc2$conf.high) + 17, 
                   xend = 4, 
                   yend = max(mod_bc2$conf.high) + 17)) + 
  geom_text(aes(x = 2.5, 
                y = max(mod_bc2$conf.high) + 23),
              label = "n.s.", size = 5)
```

@@

Fig_4C2 = ggplot(mod_bc_para2) + 
  aes(as.factor(mod_bc_para2$x),
      mod_bc_para2$predicted) + 
  geom_hline(yintercept = mean(mod_bc_para2$predicted, na.rm = T), 
             linetype = "dashed") + 
  labs(x = bquote("Parasitemia at T"[1]),
       y = "Body condition at T1") + 
  geom_errorbar(aes(ymin = mod_bc_para2$lower_CI, 
                    ymax = mod_bc_para2$higher_CI),
                colour = "black",
                size = 2, 
                width = .1) + 
  geom_errorbar(aes(ymin = mod_bc_para2$predicted - mod_bc_para2$se,
                    ymax = mod_bc_para2$predicted + mod_bc_para2$se),
                size = 8, 
                colour = wes_palette("Zissou1",5), 
                width = 0,) + 
  geom_point(color = "black", 
             size = 4) + 
  theme_classic() + 
  theme(legend.position = "none",
        axis.title = element_text(size = 20),  
        axis.title.x = element_text(size = 20, 
                                    vjust=-0.5),
        axis.text = element_text(size = 16), 
        axis.line.x = element_blank(),
        axis.ticks.x = element_blank(), 
        plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_text(hjust = 0.5, 
                                  face = "bold")) + 
  geom_segment(size = .8,
                 aes(x = 1, y = 60, xend = 5, yend = 60)) + 
    geom_text(aes(x = 3, y = 67),
              label = "P = 0.026", size = 5) + 
  geom_segment(size = .8,
                 aes(x = 1, y = 60, xend = 1, yend = 53)) + 
  geom_segment(size = .8,
                 aes(x = 5, y = 60, xend = 5, yend = 53))
```

@@

```{r summary}
## Create multipanel Figure 4
## -----------------------------------------------------------------------------
fig4 = Fig_4A + Fig_4B + Fig_4C2 + Fig_4D + plot_annotation(tag_levels = 'a') & 
  theme(plot.tag = element_text(size = 16, face = "bold"))
fig4

ggsave(fig4,filename = "./Figs/Fig4_predicted_physio_param_infection_intensities_Treatment2.png",units = "px", width = 3700, height = 3700)

@@

## Saving Figure 3
## -----------------------------------------------------------------------------
fig3 = tolres + g + plot_layout(width=c(1,2)) &  
  theme(plot.tag = element_text(size = 16, face = "bold")) 
fig3

ggsave(fig3,filename = "./Figs/Fig3.2_delta_body_condition_to_parasitemia_second.png",units = "px", width = 3700, height = 1700)

@@

ggplot(df)+
  aes(para_stage,delta_body_condition)+
  geom_boxplot()+
  geom_jitter()+
  stat_n_text()+
  geom_hline(yintercept = mean(df$delta_body_condition), linetype = 2)+
  geom_hline(yintercept = 0,colour = 'red')+
  stat_compare_means(ref.group = ".all.",hide.ns = T,method = "t.test")

@@

ggplot(df)+
    aes(treat_stage, delta_body_condition)+
    geom_hline(yintercept = mean(df$delta_body_condition), linetype = 2)+
    geom_hline(yintercept = 0,colour = 'red')+
    stat_n_text()+
    geom_boxplot()+
    stat_compare_means(comparisons = comp)

ggplot(df)+
    aes(treat_stage, Breathing_rate)+
    geom_hline(yintercept = mean(df$Breathing_rate), linetype = 2)+
    geom_hline(yintercept = 0,colour = 'red')+
    stat_n_text()+
    geom_boxplot()+
    stat_compare_means(comparisons = comp)

ggplot(df)+
    aes(treat_stage, body_temperature)+
    geom_hline(yintercept = mean(df$body_temperature), linetype = 2)+
    geom_hline(yintercept = 0,colour = 'red')+
    stat_n_text()+
    geom_boxplot()+
    stat_compare_means(comparisons = comp)

ggplot(df)+
    aes(treat_stage, Growth_rate)+
    geom_hline(yintercept = mean(df$Growth_rate), linetype = 2)+
    geom_hline(yintercept = 0,colour = 'red')+
    stat_n_text()+
    geom_boxplot()+
    stat_compare_means(comparisons = comp)
```

@@

figS1 <- Fig_S1A + Fig_S1B + Fig_S1C2 + Fig_S1D + plot_annotation(tag_levels = 'a') & 
  theme(plot.tag = element_text(size = 16, face = "bold"))
figS1

@@

ggsave(figS1,filename = "./Figs/FigS1_predicted_physio_param_infection_stages_Treatment2.png",units = "px", width = 3700, height = 3700)

@@

Fig_S2C = ggplot(df[!df$Diff_Inf_Class %in% NA,]) + 
  aes(Diff_Inf_Class,body_condition.2) + 
  geom_hline(yintercept = mean(df$body_condition.2, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "Body condition at T1") + 
  geom_jitter(color = "lightgrey", size = 2, width = .3) + 
  stat_summary(fun = mean, colour = "cornflowerblue", geom = "errorbar", 
               size = 2.8 , width = 0.05, show.legend = FALSE, 
               fun.max = function(x) mean(x) + sd(x),
               fun.min = function(x) mean(x) - sd(x)) + 
  stat_summary(fun = mean, colour = "black", geom = "point", 
               size = 5 ,show.legend = FALSE) + 
  stat_n_text() + 
  theme_classic() + 
  theme(legend.position = "none", 
        axis.title = element_text(size = 20), 
        axis.text = element_text(size = 16),
        axis.line.x = element_blank(), 
        axis.ticks.x = element_blank(),
        plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_text(hjust = 0.5, face = "bold"))

@@

## Saving Figure S2
## ----------------------------------------------------------------------------- 
figs2 = Fig_S2A + Fig_S2B + Fig_S2C + Fig_S2D + plot_annotation(tag_levels = 'a') & 
  theme(plot.tag = element_text(size = 16, face = "bold"))
figs2

ggsave(figs2,filename = "./Figs/FigS2_observed_physio_param_infection_stages_Treatment.png",units = "px", width = 3500, height = 3800)

@@

## Saving figure S3
## ----------------------------------------------------------------------------- 
figs3 = Fig_S3A + Fig_S3B + Fig_S3C + Fig_S3D + plot_annotation(tag_levels = 'a') & 
  theme(plot.tag = element_text(size = 16, face = "bold"))
figs3

ggsave(figs3,filename = "./Figs/FigS3_observed_physio_param_parasitemia_Treatment.png",units = "px", width = 3500, height = 3800)

@@

## Saving Figure S4
## ----------------------------------------------------------------------------- 
figs4 = Fig_S4A + Fig_S4B + Fig_S4C + Fig_S4D + plot_annotation(tag_levels = 'a') & 
  theme(axis.text = element_text(size=14), plot.tag = element_text(size = 16, face = "bold"))
figs4

ggsave(figs4,filename = "./Figs/FigS4_effect_sizes_param_stages.png",units = "px", width = 3500, height = 3800)

@@

## Figure S4
## ----------------------------------------------------------------------------- 
figs5 = Fig_S5A + Fig_S5B + Fig_S5C + Fig_S5D + plot_annotation(tag_levels = 'a') & 
  theme(axis.text = element_text(size=14), plot.tag = element_text(size = 16, face = "bold"))
figs5

ggsave(figs5, filename = "./Figs/FigS5_effect_sizes_param_intensities.png",units = "px", width = 3500, height = 3800)

## Additional figure: body condition at first sampling according to L. prevalence
##------------------------------------------------------------------------------

figs6 = ggplot(df)+
          aes(Prevalence1, body_condition.1)+
          geom_jitter(width=0.1)+
          geom_boxplot()+
          stat_summary(fun = mean, colour = "black", geom = "point", size = 5, show.legend = FALSE)+
          labs(x=bquote("Leucocytozoon prevalence at T"[1]),y=bquote("Body condition at T"[0]))+
          stat_compare_means(method = 't.test')

figs6

ggsave(figs6,filename = "./Figs/FigS6_body_condition_1_to_prevalence.png",units = "px", width = 3700, height = 3700)
```

## Estimating measurment error of body temperature

>>>>

```{r packages, message=F, warning=F}

require(easypackages)

libraries("chron", "cowplot","EnvStats","lsmeans","ggalt","ggdist","ggeffects",
          "ggplot2","ggpubr","ggrepel","ggridges","ggsci","ggsignif","grid",
          "gridExtra","magrittr","patchwork","plyr","rptR","RVAideMemoire",
          "sjPlot","sjlabelled","sjmisc","tidybayes","tidyverse","wesanderson",
          "car","ggh4x","ggforce","lme4","lmerTest")

## set theme for ggplot objects
theme_set(theme_tidybayes() + panel_border())
```

@@

## Panel wrapping Fig2 a & b:
## ----------------------------------------------------------------------------- 
Fig2 <-  Fig_2A +Fig_2B+
  plot_annotation(tag_levels = 'A',tag_suffix = ')') + 
  theme(plot.tag = element_text(size = 22, face = "bold"))

@@

  ggplot(mod_bc2) + 
  aes(x,predicted) + 
  geom_hline(yintercept = mean(mod_bc2$predicted, na.rm = T), 
             linetype = "dashed") + 
  labs(x = "", 
       y = bquote("Body condition at T"[1])) + 
  geom_errorbar(aes(ymin = mod_bc2$conf.low,
                    ymax = mod_bc2$conf.high),
                colour = "black",
                size = 2, 
                width = .1) +
  geom_errorbar(aes(ymin = mod_bc2$predicted - mod_bc2$std.error,
                    ymax = mod_bc2$predicted + mod_bc2$std.error),
                size = 8,
                colour = wes_palette("Zissou1",4),
                width = 0,) +
  geom_point(color = "black", 
             size = 2) + 
  theme_classic() + 
  theme(legend.position = "none",
        axis.title = element_text(size = 18),
        axis.text = element_text(size = 16),
        axis.line.x = element_blank(),
        axis.ticks.x = element_blank(),
        plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_text(hjust = 0.5, face = "bold")) + 
  geom_segment(size = .8, 
               aes(x = 1, 
                   y = max(mod_bc2$conf.high) + 17, 
                   xend = 4, 
                   yend = max(mod_bc2$conf.high) + 17)) + 
  geom_text(aes(x = 2.5, 
                y = max(mod_bc2$conf.high) + 23),
              label = "n.s.", size = 5)
```

@@

Fig_4C2 = ggplot(mod_bc_para2) + 
  aes(as.factor(mod_bc_para2$x),
      mod_bc_para2$predicted) + 
  geom_hline(yintercept = mean(mod_bc_para2$predicted, na.rm = T), 
             linetype = "dashed") + 
  labs(x = bquote("Parasitemia at T"[1]),
       y = bquote("Body condition at T"[1])) + 
  geom_errorbar(aes(ymin = mod_bc_para2$lower_CI, 
                    ymax = mod_bc_para2$higher_CI),
                colour = "black",
                size = 2, 
                width = .1) + 
  geom_errorbar(aes(ymin = mod_bc_para2$predicted - mod_bc_para2$se,
                    ymax = mod_bc_para2$predicted + mod_bc_para2$se),
                size = 8, 
                colour = wes_palette("Zissou1",5), 
                width = 0,) + 
  geom_point(color = "black", 
             size = 4) + 
  theme_classic() + 
  theme(legend.position = "none",
        axis.title = element_text(size = 20),  
        axis.title.x = element_text(size = 20, 
                                    vjust=-0.5),
        axis.text = element_text(size = 16), 
        axis.line.x = element_blank(),
        axis.ticks.x = element_blank(), 
        plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_text(hjust = 0.5, 
                                  face = "bold")) + 
  geom_segment(size = .8,
                 aes(x = 1, y = 60, xend = 5, yend = 60)) + 
    geom_text(aes(x = 3, y = 67),
              label = "P = 0.026", size = 5) + 
  geom_segment(size = .8,
                 aes(x = 1, y = 60, xend = 1, yend = 53)) + 
  geom_segment(size = .8,
                 aes(x = 5, y = 60, xend = 5, yend = 53))
```

@@

```{r summary}
## Create multipanel Figure 4
## -----------------------------------------------------------------------------
fig4 = Fig_4A + Fig_4B + Fig_4C2 + Fig_4D + plot_annotation(tag_levels = 'A', 
                  tag_suffix = ')') & 
  theme(plot.tag = element_text(size = 16, face = "bold"))
fig4

ggsave(fig4,filename = "./Figs/Fig4_predicted_physio_param_infection_intensities.png",units = "px", width = 3700, height = 3700)

@@

## Saving Figure 3
## -----------------------------------------------------------------------------
fig3 = tolres + g + plot_layout(width=c(1,2)) + plot_annotation(tag_levels = 'A',
                    tag_suffix = ')') &
  theme(plot.tag = element_text(size = 16, face = "bold")) 
fig3

ggsave(fig3,filename = "./Figs/Fig3_delta_body_condition_to_parasitemia_second.png",units = "px", width = 3700, height = 1700)

@@

g0=ggplot(df)+
  aes(para_stage,delta_body_condition)+
  geom_boxplot()+
  geom_jitter()+
  stat_n_text()+
  geom_hline(yintercept = mean(df$delta_body_condition), linetype = 2)+
  geom_hline(yintercept = 0,colour = 'red')+
  stat_compare_means(ref.group = ".all.",hide.ns = T,method = "t.test")

@@

g1=ggplot(df)+
    aes(treat_stage, delta_body_condition)+
    geom_hline(yintercept = mean(df$delta_body_condition), linetype = 2)+
    geom_hline(yintercept = 0,colour = 'red')+
    stat_n_text()+
    geom_boxplot()+
    stat_compare_means(comparisons = comp)

g2=ggplot(df)+
    aes(treat_stage, Breathing_rate)+
    geom_hline(yintercept = mean(df$Breathing_rate), linetype = 2)+
    geom_hline(yintercept = 0,colour = 'red')+
    stat_n_text()+
    geom_boxplot()+
    stat_compare_means(comparisons = comp)

g3=ggplot(df)+
    aes(treat_stage, body_temperature)+
    geom_hline(yintercept = mean(df$body_temperature), linetype = 2)+
    geom_hline(yintercept = 0,colour = 'red')+
    stat_n_text()+
    geom_boxplot()+
    stat_compare_means(comparisons = comp)

g4=ggplot(df)+
    aes(treat_stage, Growth_rate)+
    geom_hline(yintercept = mean(df$Growth_rate), linetype = 2)+
    geom_hline(yintercept = 0,colour = 'red')+
    stat_n_text()+
    geom_boxplot()+
    stat_compare_means(comparisons = comp)
```

@@

figS1 <- Fig_S1A + Fig_S1B + Fig_S1C2 + Fig_S1D + plot_annotation(tag_levels = 'A', tag_suffix = ")") & 
  theme(plot.tag = element_text(size = 16, face = "bold"))
figS1

@@

ggsave(figS1,filename = "./Figs/FigS1_predicted_physio_param_infection_stages.png",units = "px", width = 3700, height = 3700)

@@

Fig_S2C = ggplot(df[!df$Diff_Inf_Class %in% NA,]) + 
  aes(Diff_Inf_Class,body_condition.2) + 
  geom_hline(yintercept = mean(df$body_condition.2, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = bquote("Body condition at T"[1])) + 
  geom_jitter(color = "lightgrey", size = 2, width = .3) + 
  stat_summary(fun = mean, colour = "cornflowerblue", geom = "errorbar", 
               size = 2.8 , width = 0.05, show.legend = FALSE, 
               fun.max = function(x) mean(x) + sd(x),
               fun.min = function(x) mean(x) - sd(x)) + 
  stat_summary(fun = mean, colour = "black", geom = "point", 
               size = 5 ,show.legend = FALSE) + 
  stat_n_text() + 
  theme_classic() + 
  theme(legend.position = "none", 
        axis.title = element_text(size = 20), 
        axis.text = element_text(size = 16),
        axis.line.x = element_blank(), 
        axis.ticks.x = element_blank(),
        plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_text(hjust = 0.5, face = "bold"))

@@

## Saving Figure S2
## ----------------------------------------------------------------------------- 
figs2 = Fig_S2A + Fig_S2B + Fig_S2C + Fig_S2D + plot_annotation(tag_levels = 'A',
                  tag_suffix = ')') & 
  theme(plot.tag = element_text(size = 16, face = "bold"))
figs2

ggsave(figs2,filename = "./Figs/FigS2_observed_physio_param_infection_stages.png",units = "px", width = 3500, height = 3800)

@@

## Saving figure S3
## ----------------------------------------------------------------------------- 
figs3 = Fig_S3A + Fig_S3B + Fig_S3C + Fig_S3D + plot_annotation(tag_levels = 'A', tag_suffix = ')') & 
  theme(plot.tag = element_text(size = 16, face = "bold"))
figs3

ggsave(figs3,filename = "./Figs/FigS3_observed_physio_param_infection_intensities.png",units = "px", width = 3500, height = 3800)

@@

## Saving Figure S4
## ----------------------------------------------------------------------------- 
figs4 = Fig_S4A + Fig_S4B + Fig_S4C + Fig_S4D + plot_annotation(tag_levels = 'A',
                                                                tag_suffix = ')') & 
  theme(axis.text = element_text(size=14), plot.tag = element_text(size = 16, face = "bold"))
figs4

ggsave(figs4,filename = "./Figs/FigS4_effect_sizes_param_infection_stages.png",units = "px", width = 3500, height = 3800)

@@

## Figure S5: effect sizes for infection intensity models
## ----------------------------------------------------------------------------- 
figs5 = Fig_S5A + Fig_S5B + Fig_S5C + Fig_S5D + plot_annotation(tag_levels = 'A',
                                                                tag_suffix = ')') & 
  theme(axis.text = element_text(size=14), plot.tag = element_text(size = 16, face = "bold"))
figs5

ggsave(figs5, filename = "./Figs/FigS5_effect_sizes_param_infection_intensities.png",units = "px", width = 3500, height = 3800)
```

```{r robustness}
## Robustness infection stages - summary graph of third sampled individuals
##------------------------------------------------------------------------------

# Loading the dataset

third_sampled=readxl::read_excel("third_samples_indidividuals.xlsx")

# Computing the number of days between second and third sampling

third_sampled$Avg_third=third_sampled$Date.3-third_sampled$Date.2

# Categorizing infection trends

third_sampled$Stage.1_2=as.numeric(third_sampled$Infection_intensity.2)-as.numeric(third_sampled$Infection_intensity.1)

third_sampled$Stage.2_3=as.numeric(third_sampled$Infection_intensity.3)-as.numeric(third_sampled$Infection_intensity.1)

third_sampled$comp_inf_stages=NA

for(i in 1:length(third_sampled$Date.1)){
  # cat(third_sampled$Stage.1_2[i], 'versus', third_sampled$Stage.2_3[i], "\n")
  if(third_sampled$Infection_intensity.1[i] == 0 & third_sampled$Infection_intensity.2[i] == 0 &
     third_sampled$Infection_intensity.3[i]== 0){
    third_sampled$comp_inf_stages[i]="Unchanged_uninfected"
    next
  }
  if(third_sampled$Stage.1_2[i] > 0 & third_sampled$Stage.1_2[i] == third_sampled$Stage.2_3[i]){
  third_sampled$comp_inf_stages[i]="Unchanged_increase"
  next
  }
  if(third_sampled$Stage.1_2[i] < 0 & third_sampled$Stage.1_2[i] == third_sampled$Stage.2_3[i]){
    third_sampled$comp_inf_stages[i]="Unchanged_decrease"
    next
  }
  if(third_sampled$Stage.1_2[i] == 0 & third_sampled$Stage.1_2[i] == third_sampled$Stage.2_3[i]){
    third_sampled$comp_inf_stages[i]="Unchanged_stable"  
    next
  }
  if(third_sampled$Stage.1_2[i] < 0 & third_sampled$Stage.2_3[i] > 0){
    third_sampled$comp_inf_stages[i]="Decrease_to_Increase"  
    next
  }
  if(third_sampled$Stage.1_2[i] < 0 & third_sampled$Stage.2_3[i] == 0){
    third_sampled$comp_inf_stages[i]="Decrease_to_Stable" 
    next
  }
  if(third_sampled$Stage.1_2[i] == 0 & third_sampled$Stage.2_3[i] < 0){
    third_sampled$comp_inf_stages[i]="Stable_to_Decrease" 
    next
  }
  if(third_sampled$Stage.1_2[i] == 0 & third_sampled$Stage.2_3[i] > 0){
    third_sampled$comp_inf_stages[i]="Stable_to_Increase" 
    next
  }
  if(third_sampled$Stage.1_2[i] > 0 & third_sampled$Stage.2_3[i] < 0){
    third_sampled$comp_inf_stages[i]="Increase_to_decrease" 
    next
  }
  if(third_sampled$Stage.1_2[i] > 0 & third_sampled$Stage.2_3[i] == 0){
    third_sampled$comp_inf_stages[i]="Increase_to_stable" 
    next
  }
  if(third_sampled$Stage.1_2[i] > 0 & third_sampled$Stage.2_3[i] > 0){
    third_sampled$comp_inf_stages[i]="Unchanged_increase"  
    next
  }
}

third_sampled$comp_inf_stages_summary=ifelse(third_sampled$comp_inf_stages %in% c("Unchanged_increase",
                "Unchanged_decrease","Unchanged_stable",'Unchanged_uninfected'),"Unchanged","Differed")

# Plotting infection intensity across three sampling

strip=strip_themed(background_x = elem_list_rect(fill = ifelse(third_sampled$comp_inf_stages_summary %in% "Unchanged",'#30D40F','#D41C0F')))

gg_trends=ggplot(third_sampled)+
  geom_point(aes(Date.1,Infection_intensity.1))+
  geom_point(aes(Date.2,Infection_intensity.2))+
  geom_point(aes(Date.3,Infection_intensity.3))+
  facet_wrap2(~`Ring no`,scales = "free_x", strip=strip)+
  labs(title="Individual infection course - three-time sampled",x="Date",y="Infection intensity")

gg_trends

## Figure S6: Infection course - third sampled individuals
##------------------------------------------------------------------------------

ggsave(gg_trends,filename = "./Figs/FigS6_infection_trends_third_sampled.png",units = "px", width = 3700, height = 1700)

```

```{r body condition at T1 according to prevalence}
## Figure S7: body condition at first sampling according to L. prevalence
##------------------------------------------------------------------------------

figs7 = ggplot(df)+
          aes(Prevalence1, body_condition.1)+
          geom_jitter(width=0.1)+
          geom_boxplot()+
          stat_summary(fun = mean, colour = "black", geom = "point", size = 5, show.legend = FALSE)+
          labs(x=bquote("Leucocytozoon prevalence at T"[1]),y=bquote("Body condition at T"[0]))+
          stat_compare_means(method = 't.test')

figs7

ggsave(figs7,filename = "./Figs/FigS7_body_condition_T1_to_prevalence.png",units = "px", width = 3700, height = 3700)

```

## Estimating measurement error of body temperature
